Object-oriented implementations of the MPDATA advection equation solver in~C++,~Python~and~Fortran

### 2013-01-17 paper/doc/paper.tex
paper.tex: ancestor -> descendant (thanks Arjen)

  The tasks to be handled by a prototype advection equation solver proposed herein are:
  \begin{description}
    \item[(i)]{storing arrays representing the $\psi$ and $\vec{C}$ fields and any required housekeeping data,}
    \item[(ii)]{allocating and deallocating the required memory,}
    \item[(iii)]{providing access to the solver state, and}
    \item[(iv)]{performing the integration by invoking the advection-operator and
      boundary-condition handling routines.}
  \end{description}
  In the following C++ definition of the \prog{solver} structure, task (i) is represented with the definition of the structure
    member fields; task (ii) is split between the \prog{solver}'s constructor and the destructors of \prog{arrvec\_t};
    task (iii) is handled by the accessor methods; task (iv) is handled within the \prog{solve} method:
  \codecpp{code/cpp/listings.hpp}{listing08}{listing09}{1}
  The \prog{solver} structure is an abstract definition (containing a pure virtual method) 
     requiring its ancestors to implement at least
     the \prog{advop()} method which is expected to fill \prog{psi[n+1]} with the values of \prog{psi[n]} advected
     within one timestep.
  The two template parameters \prog{bcx\_t} and \prog{bcy\_t} allow the solver to operate with 
    any kind of boundary condition structures that fulfil the requirements implied by the calls to the 
    methods of \prog{bcx} and \prog{bcy}, respectively.

>>>>

  The tasks to be handled by a prototype advection equation solver proposed herein are:
  \begin{description}
    \item[(i)]{storing arrays representing the $\psi$ and $\vec{C}$ fields and any required housekeeping data,}
    \item[(ii)]{allocating and deallocating the required memory,}
    \item[(iii)]{providing access to the solver state, and}
    \item[(iv)]{performing the integration by invoking the advection-operator and
      boundary-condition handling routines.}
  \end{description}
  In the following C++ definition of the \prog{solver} structure, task (i) is represented with the definition of the structure
    member fields; task (ii) is split between the \prog{solver}'s constructor and the destructors of \prog{arrvec\_t};
    task (iii) is handled by the accessor methods; task (iv) is handled within the \prog{solve} method:
  \codecpp{code/cpp/listings.hpp}{listing08}{listing09}{1}
  The \prog{solver} structure is an abstract definition (containing a pure virtual method) 
     requiring its descendants to implement at least
     the \prog{advop()} method which is expected to fill \prog{psi[n+1]} with the values of \prog{psi[n]} advected
     within one timestep.
  The two template parameters \prog{bcx\_t} and \prog{bcy\_t} allow the solver to operate with 
    any kind of boundary condition structures that fulfil the requirements implied by the calls to the 
    methods of \prog{bcx} and \prog{bcy}, respectively.
